---
title: "Serene-Julia-Cropping"
author: "Bouzaher, Julia"
date: "April 23, 2020"
output: html_document
---

Loading packages
```{r}
library(data.table)
library(stats)
library(sf)
library(sp)
library(raster)
library(dplyr)
library(rgdal)
library(rgeos)
```

Reading in Raster File and Creating Crop Windows
```{r}

#load the land cover file once you have it in your data/ folder
landcover <- raster::raster()

# get bounds of raster file
plot(landcover)
extent(landcover)

#Documentation: testing a random small crop window

# e <- as(extent(460000, 465000, 4980000, 4990000), 'SpatialPolygons')
# crs(landcover)
# crs(e) <- "+proj=utm +zone=15 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs"
# crs(e)
# cropped2 <- raster::crop(landcover,e)
# plot(cropped2, axes = TRUE)

xmax <- 521239.5
ymax <- 5029162

#length of x and y axes - used to make tile bounds
xlength <-  521239.5 - 419971.5 
ylength <- 5029162 -  4924218

#creating x and y axes increments for making tile bounds
# y axis split into thirds, x axes split into tenths; 30 tiles total
yincrement <- ylength/3
xincrement <- xlength/10

#y crop bounds
y1 <- c(4924218, 4924218+yincrement)
y2 <- c(4924218+yincrement, 4924218+2*yincrement)
y3 <- c(4924218+2*yincrement, 5029162)

#x crop bounds
x1 <- c(xmax - xincrement, xmax)
x2 <- c(xmax - 2*xincrement, xmax - xincrement)
x3 <- c(xmax - 3*xincrement, xmax - 2*xincrement)
x4 <- c(xmax - 4*xincrement, xmax - 3*xincrement)
x5 <- c(xmax - 5*xincrement, xmax - 4*xincrement)
x6 <- c(xmax - 6*xincrement, xmax - 5*xincrement)
x7 <- c(xmax - 7*xincrement, xmax - 6*xincrement)
x8 <- c(xmax - 8*xincrement, xmax - 7*xincrement)
x9 <- c(xmax - 9*xincrement, xmax - 8*xincrement)
x10 <- c(xmax - 10*xincrement, xmax - 9*xincrement)

#we want to split x into 10 and y into 3 fto obtain 30 blocks total
#format is : xmin, xmax, ymin, ymax. shortened into (xrange, yrange with premade objects above)

crop1 <- as(extent(x1,y1), 'SpatialPolygons')
crop2 <- as(extent(x2,y1), 'SpatialPolygons')
crop3 <- as(extent(x3,y1), 'SpatialPolygons')
crop4 <- as(extent(x4,y1), 'SpatialPolygons')
crop5 <- as(extent(x5,y1), 'SpatialPolygons')
crop6 <- as(extent(x6,y1), 'SpatialPolygons')
crop7 <- as(extent(x7,y1), 'SpatialPolygons')
crop8 <- as(extent(x8,y1), 'SpatialPolygons')
crop9 <- as(extent(x9,y1), 'SpatialPolygons')
crop10 <- as(extent(x10,y1), 'SpatialPolygons')
crop11 <- as(extent(x1,y2), 'SpatialPolygons')
crop12 <- as(extent(x2,y2), 'SpatialPolygons')
crop13 <- as(extent(x3,y2), 'SpatialPolygons')
crop14 <- as(extent(x4,y2), 'SpatialPolygons')
crop15 <- as(extent(x5,y2), 'SpatialPolygons')
crop16 <- as(extent(x6,y2), 'SpatialPolygons')
crop17 <- as(extent(x7,y2), 'SpatialPolygons')
crop18 <- as(extent(x8,y2), 'SpatialPolygons')
crop19 <- as(extent(x9,y2), 'SpatialPolygons')
crop20 <- as(extent(x10,y2), 'SpatialPolygons')
crop21 <- as(extent(x1,y3), 'SpatialPolygons')
crop22 <- as(extent(x2,y3), 'SpatialPolygons')
crop23 <- as(extent(x3,y3), 'SpatialPolygons')
crop24 <- as(extent(x4,y3), 'SpatialPolygons')
crop25 <- as(extent(x5,y3), 'SpatialPolygons')
crop26 <- as(extent(x6,y3), 'SpatialPolygons')
crop27 <- as(extent(x7,y3), 'SpatialPolygons')
crop28 <- as(extent(x8,y3), 'SpatialPolygons')
crop29 <- as(extent(x9,y3), 'SpatialPolygons')
crop30 <- as(extent(x10,y3), 'SpatialPolygons')

```


Increasing memory limit to deal with raster conversion
```{r}
memory.limit(size = 100000000000000000000)
memory.size(max = NA)
```


Cropping the raster dataframes ("land") with the bounds created above ("crop")
```{r}
land1 <- raster::crop(landcover,crop1)
land2 <- raster::crop(landcover,crop2)
land3 <- raster::crop(landcover,crop3)
land4 <- raster::crop(landcover,crop4)
land5 <- raster::crop(landcover,crop5)
land6 <- raster::crop(landcover,crop6)
land7 <- raster::crop(landcover,crop7)
land8 <- raster::crop(landcover,crop8)
land9 <- raster::crop(landcover,crop9)
land10 <- raster::crop(landcover,crop10)
land11 <- raster::crop(landcover,crop11)
land12 <- raster::crop(landcover,crop12)
land13 <- raster::crop(landcover,crop13)
land14 <- raster::crop(landcover,crop14)
land15 <- raster::crop(landcover,crop15)
land16 <- raster::crop(landcover,crop16)
land17 <- raster::crop(landcover,crop17)
land18 <- raster::crop(landcover,crop18)
land19 <- raster::crop(landcover,crop19)
land20 <- raster::crop(landcover,crop20)
land21 <- raster::crop(landcover,crop21)
land22 <- raster::crop(landcover,crop22)
land23 <- raster::crop(landcover,crop23)
land24 <- raster::crop(landcover,crop24)
land25 <- raster::crop(landcover,crop25)
land26 <- raster::crop(landcover,crop26)
land27 <- raster::crop(landcover,crop27)
land28 <- raster::crop(landcover,crop28)
land29 <- raster::crop(landcover,crop29)
land30 <- raster::crop(landcover,crop30)

```

Code for saving the Raster-as-dataframes (all at once) : Over 230 GB worth of files
```{r}

tile1 <- raster::as.data.frame(land1, xy = TRUE)
tile2 <- raster::as.data.frame(land2, xy = TRUE)
tile3 <- raster::as.data.frame(land3, xy = TRUE)
tile4 <- raster::as.data.frame(land4, xy = TRUE)
tile5 <- raster::as.data.frame(land5, xy = TRUE)
tile6 <- raster::as.data.frame(land6, xy = TRUE)
tile7 <- raster::as.data.frame(land7, xy = TRUE)
tile8 <- raster::as.data.frame(land8, xy = TRUE)
tile9 <- raster::as.data.frame(land9, xy = TRUE)
tile10 <- raster::as.data.frame(land10, xy = TRUE)
tile11 <- raster::as.data.frame(land11, xy = TRUE)
tile12 <- raster::as.data.frame(land12, xy = TRUE)
tile13 <- raster::as.data.frame(land13, xy = TRUE)
tile14 <- raster::as.data.frame(land14, xy = TRUE)
tile15 <- raster::as.data.frame(land15, xy = TRUE)
tile16 <- raster::as.data.frame(land16, xy = TRUE)
tile17 <- raster::as.data.frame(land17, xy = TRUE)
tile18 <- raster::as.data.frame(land18, xy = TRUE)
tile19 <- raster::as.data.frame(land19, xy = TRUE)
tile20 <- raster::as.data.frame(land20, xy = TRUE)
tile21 <- raster::as.data.frame(land21, xy = TRUE)
tile22 <- raster::as.data.frame(land22, xy = TRUE)
tile23 <- raster::as.data.frame(land23, xy = TRUE)
tile24 <- raster::as.data.frame(land24, xy = TRUE)
tile25 <- raster::as.data.frame(land25, xy = TRUE)
tile26 <- raster::as.data.frame(land26, xy = TRUE)
tile27 <- raster::as.data.frame(land27, xy = TRUE)
tile28 <- raster::as.data.frame(land28, xy = TRUE)
tile29 <- raster::as.data.frame(land29, xy = TRUE)
tile30 <- raster::as.data.frame(land30, xy = TRUE)

```

Code for saving the Raster-as-dataframes (one at a time): Over 230 GB worth of files
```{r}
land1 <- raster::raster("land1.tif", RAT = TRUE)
tile1 <- raster::as.data.frame(land1, xy = TRUE)
remove(land1)
fwrite(tile1, "tile1.txt")
remove(tile1)

land2 <- raster::raster("land2.tif", RAT = TRUE)
tile2 <- raster::as.data.frame(land2, xy = TRUE)
remove(land2)
fwrite(tile2, "tile2.txt")
remove(tile2)

land3 <- raster::raster("land3.tif", RAT = TRUE)
tile3 <- raster::as.data.frame(land3, xy = TRUE)
remove(land3)
fwrite(tile3, "tile3.txt")
remove(tile3)

land4 <- raster::raster("land4.tif", RAT = TRUE)
tile4 <- raster::as.data.frame(land4, xy = TRUE)
remove(land4)
fwrite(tile4, "tile4.txt")
remove(tile4)

land5 <- raster::raster("land5.tif", RAT = TRUE)
tile5 <- raster::as.data.frame(land5, xy = TRUE)
remove(land5)
fwrite(tile5, "tile5.txt")
remove(tile5)

land6 <- raster::raster("land6.tif", RAT = TRUE)
tile6 <- raster::as.data.frame(land6, xy = TRUE)
remove(land6)
fwrite(tile6, "tile6.txt")
remove(tile6)

land7 <- raster::raster("land7.tif", RAT = TRUE)
tile7 <- raster::as.data.frame(land7, xy = TRUE)
remove(land7)
fwrite(tile7, "tile7.txt")
remove(tile7)

land8 <- raster::raster("land8.tif", RAT = TRUE)
tile8 <- raster::as.data.frame(land8, xy = TRUE)
remove(land8)
fwrite(tile8, "tile8.txt")
remove(tile8)

land9 <- raster::raster("land9.tif", RAT = TRUE)
tile9 <- raster::as.data.frame(land9, xy = TRUE)
remove(land9)
fwrite(tile9, "tile9.txt")
remove(tile9)

land10 <- raster::raster("land10.tif", RAT = TRUE)
tile10 <- raster::as.data.frame(land10, xy = TRUE)
remove(land10)
fwrite(tile10, "tile10.txt")
remove(tile10)

land11 <- raster::raster("land11.tif", RAT = TRUE)
tile11 <- raster::as.data.frame(land11, xy = TRUE)
remove(land11)
fwrite(tile11, "tile11.txt")
remove(tile11)

land12 <- raster::raster("land12.tif", RAT = TRUE)
tile12 <- raster::as.data.frame(land12, xy = TRUE)
remove(land12)
fwrite(tile12, "tile12.txt")
remove(tile12)


land13 <- raster::raster("land13.tif", RAT = TRUE)
tile13 <- raster::as.data.frame(land13, xy = TRUE)
remove(land13)
fwrite(tile13, "tile13.txt")
remove(tile13)

land14 <- raster::raster("land14.tif", RAT = TRUE)
tile14 <- raster::as.data.frame(land14, xy = TRUE)
remove(land14)
fwrite(tile14, "tile14.txt")
remove(tile14)

land15 <- raster::raster("land15.tif", RAT = TRUE)
tile15 <- raster::as.data.frame(land15, xy = TRUE)
remove(land15)
fwrite(tile15, "tile15.txt")
remove(tile15)

land16 <- raster::raster("land16.tif", RAT = TRUE)
tile16 <- raster::as.data.frame(land16, xy = TRUE)
remove(land16)
fwrite(tile16, "tile16.txt")
remove(tile16)

land17 <- raster::raster("land17.tif", RAT = TRUE)
tile17 <- raster::as.data.frame(land17, xy = TRUE)
remove(land17)
fwrite(tile17, "tile17.txt")
remove(tile17)

land18 <- raster::raster("land18.tif", RAT = TRUE)
tile18 <- raster::as.data.frame(land18, xy = TRUE)
remove(land18)
fwrite(tile18, "tile18.txt")
remove(tile18)

land19 <- raster::raster("land19.tif", RAT = TRUE)
tile19 <- raster::as.data.frame(land19, xy = TRUE)
remove(land19)
fwrite(tile19, "tile19.txt")
remove(tile19)

land20 <- raster::raster("land20.tif", RAT = TRUE)
tile20 <- raster::as.data.frame(land20, xy = TRUE)
remove(land20)
fwrite(tile20, "tile20.txt")
remove(tile20)

land21 <- raster::raster("land21.tif", RAT = TRUE)
tile21 <- raster::as.data.frame(land21, xy = TRUE)
remove(land21)
fwrite(tile21, "tile21.txt")
remove(tile21)

land22 <- raster::raster("land22.tif", RAT = TRUE)
tile22 <- raster::as.data.frame(land22, xy = TRUE)
remove(land22)
fwrite(tile22, "tile22.txt")
remove(tile22)

land23 <- raster::raster("land23.tif", RAT = TRUE)
tile23 <- raster::as.data.frame(land23, xy = TRUE)
remove(land23)
fwrite(tile23, "tile23.txt")
remove(tile23)

land24 <- raster::raster("land24.tif", RAT = TRUE)
tile24 <- raster::as.data.frame(land24, xy = TRUE)
remove(land24)
fwrite(tile24, "tile24.txt")
remove(tile24)

land25 <- raster::raster("land25.tif", RAT = TRUE)
tile25 <- raster::as.data.frame(land25, xy = TRUE)
remove(land25)
fwrite(tile25, "tile25.txt")
remove(tile25)

land26 <- raster::raster("land26.tif", RAT = TRUE)
tile26 <- raster::as.data.frame(land26, xy = TRUE)
remove(land26)
fwrite(tile26, "tile26.txt")
remove(tile26)

land27 <- raster::raster("land27.tif", RAT = TRUE)
tile27 <- raster::as.data.frame(land27, xy = TRUE)
remove(land27)
fwrite(tile27, "tile27.txt")
remove(tile27)

land28 <- raster::raster("land28.tif", RAT = TRUE)
tile28 <- raster::as.data.frame(land28, xy = TRUE)
remove(land28)
fwrite(tile28, "tile28.txt")
remove(tile28)


land29 <- raster::raster("land29.tif", RAT = TRUE)
tile29 <- raster::as.data.frame(land29, xy = TRUE)
remove(land29)
fwrite(tile29, "tile29.txt")
remove(tile29)

land30 <- raster::raster("land30.tif", RAT = TRUE)
tile30 <- raster::as.data.frame(land30, xy = TRUE)
remove(land30)
fwrite(tile30, "tile30.txt")
remove(tile30)

```

Run this chunk if you need to load in the raster files.
```{r} 
land1 <- raster::raster("land1.tif", RAT = TRUE)
land2 <- raster::raster("land2.tif", RAT = TRUE)
land3 <- raster::raster("land3.tif", RAT = TRUE)
land4 <- raster::raster("land4.tif", RAT = TRUE)
land5 <- raster::raster("land5.tif", RAT = TRUE)
land6 <- raster::raster("land6.tif", RAT = TRUE)
land7 <- raster::raster("land7.tif", RAT = TRUE)
land8 <- raster::raster("land8.tif", RAT = TRUE)
land9 <- raster::raster("land9.tif", RAT = TRUE)
land10 <- raster::raster("land10.tif", RAT = TRUE)
land11 <- raster::raster("land11.tif", RAT = TRUE)
land12 <- raster::raster("land12.tif", RAT = TRUE)
land13 <- raster::raster("land13.tif", RAT = TRUE)
land14 <- raster::raster("land14.tif", RAT = TRUE)
land15 <- raster::raster("land15.tif", RAT = TRUE)
land16 <- raster::raster("land16.tif", RAT = TRUE)
land17 <- raster::raster("land17.tif", RAT = TRUE)
land18 <- raster::raster("land18.tif", RAT = TRUE)
land19 <- raster::raster("land19.tif", RAT = TRUE)
land20 <- raster::raster("land20.tif", RAT = TRUE)
land21 <- raster::raster("land21.tif", RAT = TRUE)
land22 <- raster::raster("land22.tif", RAT = TRUE)
land23 <- raster::raster("land23.tif", RAT = TRUE)
land24 <- raster::raster("land24.tif", RAT = TRUE)
land25 <- raster::raster("land25.tif", RAT = TRUE)
land26 <- raster::raster("land26.tif", RAT = TRUE)
land27 <- raster::raster("land27.tif", RAT = TRUE)
land28 <- raster::raster("land28.tif", RAT = TRUE)
land29 <- raster::raster("land29.tif", RAT = TRUE)
land30 <- raster::raster("land30.tif", RAT = TRUE)
```


Julia's chunk for reading in tiles from local data drive.
```{r}
library(data.table)
tile1 <- fread("E:/tiles/tile1.txt", drop = c(1:2))
tile2 <- fread("E:/tiles/tile2.txt", drop = c(1:2))
tile3 <- fread("E:/tiles/tile3.txt", drop = c(1:2))
tile4 <- fread("E:/tiles/tile4.txt", drop = c(1:2))
tile5 <- fread("E:/tiles/tile5.txt", drop = c(1:2))
tile6 <- fread("E:/tiles/tile6.txt", drop = c(1:2))
tile7 <- fread("E:/tiles/tile7.txt", drop = c(1:2))
tile8 <- fread("E:/tiles/tile8.txt", drop = c(1:2))
tile9 <- fread("E:/tiles/tile9.txt", drop = c(1:2))
tile10 <- fread("E:/tiles/tile10.txt", drop = c(1:2))
tile11 <- fread("E:/tiles/tile11.txt", drop = c(1:2))
tile12 <- fread("E:/tiles/tile12.txt", drop = c(1:2))
tile13 <- fread("E:/tiles/tile13.txt", drop = c(1:2))
tile14 <- fread("E:/tiles/tile14.txt", drop = c(1:2))
tile15 <- fread("E:/tiles/tile15.txt", drop = c(1:2))
tile16 <- fread("E:/tiles/tile16.txt", drop = c(1:2))
tile17 <- fread("E:/tiles/tile17.txt", drop = c(1:2))
tile18 <- fread("E:/tiles/tile18.txt", drop = c(1:2))
tile19 <- fread("E:/tiles/tile19.txt", drop = c(1:2))
tile20 <- fread("E:/tiles/tile20.txt", drop = c(1:2))
tile21 <- fread("E:/tiles/tile21.txt", drop = c(1:2))
tile22 <- fread("E:/tiles/tile22.txt", drop = c(1:2))
tile23 <- fread("E:/tiles/tile23.txt", drop = c(1:2))
tile24 <- fread("E:/tiles/tile24.txt", drop = c(1:2))
tile25 <- fread("E:/tiles/tile25.txt", drop = c(1:2))
tile26 <- fread("E:/tiles/tile26.txt", drop = c(1:2))
tile27 <- fread("E:/tiles/tile27.txt", drop = c(1:2))
tile28 <- fread("E:/tiles/tile28.txt", drop = c(1:2))
tile29 <- fread("E:/tiles/tile29.txt", drop = c(1:2))
tile30 <- fread("E:/tiles/tile30.txt", drop = c(1:2))

```


Examining Raster-as-dataframe tile
```{r}
head(tile1)
#    a
# 1: 8
# 2: 8
# 3: 8
# 4: 8
# 5: 8
# 6: 8
unique(tile1$a)
class(tile1$a)
# 
# > unique(tile1$a)
#  [1]  8  6  1  4  7 11  0  3  9 10  5  2 12
# > class(tile1$a)
# [1] "integer"
```


Increase Memory Limit Again if Needed to Run Loop
```{r}
memory.limit(size = 100000000000000000000)
memory.size(max = NA)
```


Rough Draft of Regional Land Cover Counts Table - Documentation
```{r}

#Count tabulation function draft

#loop with if statement
# load tile i
# summarize and count categories for tile i
# add these counts to table A: categories 0-12
# delete tile i
# loop: load next tile i

#length of loop : 30
#:length of table A is : 12


#intialize structures for the loop
listfiles <- Sys.glob(file.path("E:/tiles/", "*.txt"))
final_data <- data.frame(var = c(1:13), num = c(0,0,0,0,0,0,0,0,0,0,0,0,0))
library(stats)

for (i in 1:30){
  #load in tile i
  new_data <- fread(listfiles[i]) %>%
  #fix colnames
  setNames(c("x", "y", "a")) %>%
  # summarize and count categories for tile i
  group_by(a) %>%
  summarize(count = n())
  # add these counts to table A: categories 0-12
  final_data$num <- final_data$num + new_data$count
  # delete tile i
  #remove(new_data)
# loop: load next tile i
}

#Alternative Loop Option (Not Used)
# 
# final_data <- data.frame(var = c(0:12), num = c(0,0,0,0,0,0,0,0,0,0,0,0,0))
# 
# for (i in 1:30){  new_data <- fread(listfiles[i])
#   for(j in 1:nrow(new_data)){
#     final_data <- final_data %>% 
#       mutate(num = case_when(
#         var == new_data[j,] ~ num +1,
#         TRUE ~ num
#         ))
#     }
#}


final_data
# 
#    var        num
# 1    1 2922927079
# 2    2 2311941475
# 3    3  713179481
# 4    4  964031672
# 5    5 1529041012
# 6    6 1151912655
# 7    7 2369823175
# 8    8  820881998
# 9    9 2498075451
# 10  10 1326997672
# 11  11  995635847
# 12  12  808214555
# 13  13 2127074591

total <- sum(final_data$num)
# total
# [1] 20539736663
```


Final Loop and Regional Land Cover Counts Table Generation
```{r}
#clear memory and increase memory size again
memory.limit(size = 1000000000000000000)
memory.size(max = NA)
gc()

#Reload essential packages
library(stats)
library(dplyr)
library(data.table)

#Initialize list of files and empty data tables to record counts by land cover classification for r
listfiles <- Sys.glob(file.path("E:/tiles/", "*.txt"))
final_data <- data.frame(var = c(0:12), num = c(0,0,0,0,0,0,0,0,0,0,0,0,0))
final_data2 <- data.frame(var = c(0:12), num = c(0,0,0,0,0,0,0,0,0,0,0,0,0))
final_data3 <- data.frame(var = c(0:12), num = c(0,0,0,0,0,0,0,0,0,0,0,0,0))

#Loop Used to Create final_counts.csv
# Default form below, but Julia had to alter it 3 times through three tables initialized above: final_data, final_data2, final_data3

for (i in 1:30){
  #load in tile i
  new_data <- fread(listfiles[i], drop = (1:2)) %>%
  #fix colnames
  setNames(c("a")) 
  new_data$a <- factor(new_data$a, levels= 1:12)
  # summarize and count categories for tile i
  new_data <- new_data %>%
  count(a, .drop = FALSE) 
  # add these counts to table A: categories 0-12
  final_data$num <- final_data3$num + new_data$n
  # delete tile i
  #remove(new_data)
# loop: load next tile i
}

#Single Tile Count Table Generation (used when the loop stopped at Iteration 29)
new_data <- tile30 %>% setNames(c("a"))
new_data$a <-  factor(new_data$a, levels= 1:12)
  # summarize and count categories for tile i
 new_data <- new_data %>%
  count(a, .drop = FALSE)
  # add these counts to table A: categories 0-12
  final_data3$num <- final_data3$num + new_data$n

  
#final_data: 1-21 
total1 <- sum(final_data$num)
total1/354262714
#20.99
#21 iterations in final_data
  
#final_data2: 21-29
total2 <- sum(final_data2$num)
total2/354262714
#7.99
#8 iterations in final_data2

#final_data2: 30
total3 <- sum(final_data3$num)
total3/354262714
#1
#1 final iteration in final_data3

total <- total1 + total2 + total3
total
#10627479119

#theoretical total:
#1 tile's amount of rows * 30 tiles
354262714*30
#10627881420

#match!
(10627881420-10627479119)/10627479119 *100
# almost complete match ... .3% difference

final_counts <- final_data + final_data2 + final_data3
final_counts$var <- final_counts$var/3
#check
sum(final_counts$num)
#10627479119


#Making final table
final_counts <- final_counts %>%
  mutate(percent = (num/total)*100) %>%
  rename(id = var) %>% 
  arrange(id) %>%
  mutate(landcover = c("NA", "Grass/Shrub", "Bare Soil", "Buildings", "Roads/Paved Surfaces", "Lakes/Ponds", "Deciduous Tree Canopy", "Coniferous Tree Canopy", "Agriculture", "Emergent Wetland", "Forested/Shrub Wetland", "River", "Extraction"))


#Generate final Regional counts csv
write.csv(final_counts, file = "final_counts.csv")


#Reference: Landcover classification legend
# "O": "NA"
#“1” = “Grass/Shrub”,
# “2” = “Bare Soil”,
# “3” = “Buildings”,
# “4” = “Roads/Paved Surfaces”,
# “5” = “Lakes/Ponds”,
# “6” = “Deciduous Tree Canopy”,
# “7” = “Coniferous Tree Canopy”,
# “8” = “Agriculture”,
# “9” = “Emergent Wetland”,
# “10” = “Forested/Shrub Wetland”,
# “11” = “River”,
# “12” = “Extraction”

```


```{r}
#re-assign landcover categories to account for NA
final <- read_csv("final_counts.csv") %>% 
  mutate(landcover = lead(landcover), id = case_when(
    id == 12~ 0,
    TRUE ~lead(id)))

write.csv(final, file = "final_counts_fixed.csv")
```

